\documentclass[11pt]{article}
\usepackage{lmodern}

\usepackage[T1]{fontenc}
\usepackage{inter}
\renewcommand*\familydefault{\sfdefault}

\usepackage{geometry}
\geometry{
    a4paper,
    top=1.8cm,
    bottom=1in,
    left=2.5cm,
    right=2.5cm
}

\setcounter{secnumdepth}{0}
\pdfgentounicode=1

\usepackage{enumitem}
\setlist[itemize]{
    noitemsep,
    left=2em
}
\setlist[description]{itemsep=0pt}
\setlist[enumerate]{align=left}
\usepackage[dvipsnames]{xcolor}
\definecolor{icnclr}{rgb}{0.4, 0.65, 0.85}
\definecolor{blue1}{rgb}{0.2, 0.2, 0.6}
\definecolor{blue2}{rgb}{0.25, 0.35, 0.65}
\usepackage{titlesec}
\titlespacing{\subsection}{0pt}{*0}{*0}
\titlespacing{\subsubsection}{0pt}{*0}{*0}
\titleformat{\section}{\color{blue1}\large\fontseries{black}\selectfont\uppercase}{}{}{\ruleafter}[\global\RemVStrue]
\titleformat{\subsection}{\color{blue2}\fontseries{bold}\selectfont}{}{}{\rvs}
\titleformat{\subsubsection}{\color{icnclr}\fontseries{}\selectfont}{}{}{}

\usepackage{xhfill}
\newcommand\ruleafter[1]{#1~\xrfill[.5ex]{1pt}[gray]}

\newif\ifRemVS
\newcommand{\rvs}{
    \ifRemVS
        \vspace{-1.5ex}
    \fi
    \global\RemVSfalse
}

\usepackage{fontawesome5}

\usepackage[bookmarks=false]{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=Sepia,
    pdftitle={Daehyun Jang CV},
}

\usepackage[page]{totalcount}
\usepackage{fancyhdr}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\fancyhf{}

\usepackage{datetime}
\newdateformat{mydate}{\shortmonthname[\THEMONTH]. \THEDAY. \THEYEAR}

\usepackage{amsmath}
\usepackage{amsfonts}

\begin{document}

\begin{center}
{\fontsize{28}{28}\selectfont Daehyun Jang} \\ \bigskip
\vspace{-1cm}{\hfill \small CV Ver:\\\hfill\mydate\today} \\
{\color{blue2}\faMapMarker} Seoul, Republic of Korea \quad
{\color{blue2}\faEnvelope[regular]} \href{mailto:jadh0309@snu.ac.kr}{jadh0309@snu.ac.kr}
\end{center}

\section{About Me}
I am a Ph.D. student in Mathematical Sciences at Seoul National University, advised by Prof. \href{https://web.math.snu.ac.kr/~jhcheon/}{Jung Hee Cheon}.
My research focuses on Cryptography, particularly Homomorphic Encryption.

\section{Education}

        \subsection{Integrated M.S./Ph.D. Program in Mathematical Sciences \hfill \textcolor{black}{\normalfont Sep. 2024 -- Present}}
                \subsubsection{Seoul National University, Seoul, Republic of Korea}

        \subsection{B.S. in Mathematical Sciences \hfill \textcolor{black}{\normalfont Mar. 2019 -- Aug. 2024}}
            \subsubsection{Seoul National University, Seoul, Republic of Korea}
            \begin{itemize}
                \item \textit{GPA}: 3.86/4.3 (Overall)
                    \begin{itemize}
                        \item \textit{Major}: Mathematical Sciences (3.99/4.3)
                        \item \textit{Minor}: Philosophy (3.80/4.3)
                    \end{itemize}
                \item {\small \textit{Military Service} at Republic of Korea Army \hfill \normalfont Dec. 2020 -- Jun. 2022}
            \end{itemize}

\section{Publications}

\subsection{Published}
\begin{itemize}
    \item Jung Hee Cheon, {\bf Daehyun Jang}, ``Cryptanalysis on Lightweight Verifiable Homomorphic Encryption,'' \textit{Asiacrypt 2025}.\\
    {\footnotesize\textit{Author order is alphabetical by surname.}}
\end{itemize}

\subsection{Preprint(s)}
    \begin{itemize}
        \item Jung Hee Cheon, {\bf Daehyun Jang}, Jaehee Kang, Hanee Rhee, ``Private Embedding Lookup with Encrypted Compact Queries under Fully Homomorphic Encryption''\\
        {\footnotesize\textit{Author order is alphabetical by surname.}}
        \item Jung Hee Cheon, {\bf Daehyun Jang}, Jaehee Kang, Hanee Rhee, ``SWIFT: Shallow and SIMD-Aware CKKS Functional Bootstrapping for Low-Latency''\\
        {\footnotesize\textit{Author order is alphabetical by surname.}}
    \end{itemize}

\section{Talks}
\begin{itemize}
    \item Korean Mathematical Society (KMS) 2024 Fall Meeting\\
    ``Cryptanalysis on Lightweight Verifiable Homomorphic Encryption''
    \item Asiacrypt 2025\\
    ``Cryptanalysis on Lightweight Verifiable Homomorphic Encryption''
    \item International Conference for the 80th Anniversary of the Korean Mathematical Society\\
    {\small Jun. 23, 2026}\\
    ``SWIFT: Shallow and SIMD-Aware CKKS Functional Bootstrapping\\
    for Low-Latency''
    \item PACOH Workshop: Homomorphic Encryption 2026\\
    {\small Jun. 29, 2026, Sokcho, Republic of Korea}\\
    ``SWIFT: Shallow and SIMD-Aware CKKS Functional Bootstrapping\\
    for Low-Latency''
\end{itemize}

\section{Posters}
\begin{itemize}
    \item FHE.org Conference 2026, ``Efficient Private Embedding Lookup via Independent Vector Evaluation''
\end{itemize}

\section{Research Internship}

\subsection{Graduate Research Fellow}
\subsubsection{Korea Institute for Advanced Study (KIAS), Seoul, Republic of Korea}
\begin{itemize}
    \item Homomorphic Encryption \hfill Jan. 2025 -- Present
    \begin{itemize}
        \item Theoretical study on the CKKS scheme
        \item Advised by Prof. Jeong Han Kim
    \end{itemize}
\end{itemize}

\subsection{Undergraduate Research Internship}
\subsubsection{Seoul National University, Seoul, Republic of Korea}
\begin{itemize}
    \item Homomorphic Encryption \hfill Oct. 2023 -- Aug. 2024
    \begin{itemize}
        \item Study on the CKKS scheme and its recent advances
        \item Advised by Prof. Jung Hee Cheon
    \end{itemize}

    \item Homogeneous Dynamics \hfill Jun. 2023 -- Aug. 2023
    \begin{itemize}
        \item Study on the Quantitative version of the Oppenheim conjecture
        \item Advised by Prof. Seonhee Lim
    \end{itemize}
\end{itemize}

\section{Teaching Experience}

\subsection{Teaching Assistant}
\begin{itemize}
    \item Abstract Algebra I \hfill Spring 2026
    \item Engineering Mathematics I \hfill Spring 2026
    \item Mathematical Exercises II \hfill Fall 2024, Fall 2025
    \item Advanced Mathematical Exercises I \hfill Spring 2025
\end{itemize}

\subsection{Undergraduate Tutor}
\begin{itemize}
    \item Mathematics I \hfill Spring 2020, Spring 2024
    \item Mathematics II \hfill Fall 2020
    \item Mathematics for Life Sciences I \hfill Spring 2023
    \item Calculus II \hfill Fall 2023
\end{itemize}

\section{Honors \& Awards}
\begin{itemize}
\item 3rd Place, Korea Crypto Contest \hfill Oct. 2025
\item Outstanding Teaching Assistant Award, Seoul National University \hfill Dec. 2024
\item Outstanding Tutor Award, Seoul National University \hfill Dec. 2023
\item Outstanding Student Award, Seoul National University \hfill Dec. 2020
\end{itemize}

\end{document}
